Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-02 Manuscript/manuscript.tex
Modified and polished sections Intro and Methods. Introduced extra fixes and updated NaCl figure.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.5cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: The chemical structure of POPC and the labeling of the carbon segments.
    Middle: Order parameters of POPC head group, glycerol backbone and acyl chains 
    from simulations with the Lipid14 \cite{dickson14} and the ECC-lipid models
    compared with the experimental values from \cite{ferreira13}.
    The size of the points for the head group order parameters correspond 
    the error bars ($\pm 0.02$ for experiments \cite{botan15,ollila16} and ?? for
    simulations {\bf Add the size of the error bars in simulations.}).
    The size of the points for acyl chains are decreased by a factor of 3 to improve the clarity of the plot.
    Bottom: X-ray scattering form factors from simulations with the Lipid14 \cite{dickson14} and
    the ECC-lipid models compared with experiments~\cite{Kucerka2011}.
  } 
  \todo{Increase the height of the order parameter figure} \\
  \todo{sn-1 and sn-2 order parameters should be somehow labelled in the order parameter figure. Maybe empty and filled points?} \\
  \todo{Would it be possible to increase the size of points for acyl chain order parameters only in z-direction such that
    it would correspond the error bars?} \\
  \todo{x-axis in form factor plot from 0 to 0.6, where experimental data ends. y-axis from 0 to $\sim$2.2 to remove the empty space.} \\
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/density_profiles_ca_cl_wat_phos_models-compar.pdf}
  \caption{\label{fig:cacl-dens}
    Number density profiles of \ce{Ca^{2+}}, \ce{Na^{+}} and \ce{Cl^-} along membrane normal axis
    for different force fields. Data for Lipid14 with \AA{}qvist ions are taken directly from Ref. \citenum{catte16}.
    %Normalization factor for ions is 1 for monovalent ions (i.e.~\ce{Na^+} and~\ce{Cl^-}),
    In order to visualize the density profiles with a scale comparable to the profile of \ce{Ca^{2+}}, 
    densities of~\ce{Cl^-} and \ce{Na^{+}} are divided by 2, and
    densities of phosphate group resp. water are divided by 5 resp. 200. 
    The molar concentration of ions in water is 350~mM in all systems
    presented here. 
    }
  \todo{PAVEL: include the number of$\Gamma$-surface access.} \\
\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.2cm]{../Fig/ipython_nb/Order-parameters_form-factors_exp-L14-ECCL17_q80_sig89.pdf}
  \includegraphics[width=7.4cm]{../Fig/POPCstructure.eps}
  %\includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  %\includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: The chemical structure of POPC and the labeling of the carbon segments.
    Middle: Order parameters of POPC head group, glycerol backbone and acyl chains 
    from simulations with the Lipid14 \cite{dickson14} and the ECC-lipid models
    compared with the experimental values from \cite{ferreira13}.
    The size of the points for the head group order parameters correspond 
    the error bars ($\pm 0.02$ for experiments \cite{botan15,ollila16} and ?? for
    simulations {\bf Add the size of the error bars in simulations.}).
    The size of the points for acyl chains are decreased by a factor of 3 to improve the clarity of the plot.
    Bottom: X-ray scattering form factors from simulations with the Lipid14 \cite{dickson14} and
    the ECC-lipid models compared with experiments~\cite{Kucerka2011}.
  } 
  \todo{Increase the height of the order parameter figure} \\
  \todo{sn-1 and sn-2 order parameters should be somehow labelled in the order parameter figure. Maybe empty and filled points?} \\
  \todo{Would it be possible to increase the size of points for acyl chain order parameters only in z-direction such that
    it would correspond the error bars?} \\
  \todo{x-axis in form factor plot from 0 to 0.6, where experimental data ends. y-axis from 0 to $\sim$2.2 to remove the empty space.} \\
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[height=20.0cm]{../Fig/ipython_nb/density_profiles_ca_cl_wat_phos_models-compar.pdf}
  \caption{\label{fig:cacl-dens}
    Number density profiles of \ce{Ca^{2+}}, \ce{Na^{+}} and \ce{Cl^-} along membrane normal axis
    for different force fields. Data for Lipid14 with \AA{}qvist ions are taken directly from Ref. \citenum{catte16}.
    %Normalization factor for ions is 1 for monovalent ions (i.e.~\ce{Na^+} and~\ce{Cl^-}),
    In order to visualize the density profiles with a scale comparable to the profile of \ce{Ca^{2+}}, 
    densities of~\ce{Cl^-} and \ce{Na^{+}} are divided by 2, and
    densities of phosphate group resp. water are divided by 5 resp. 200. 
    The molar concentration of ions in water is 350~mM in all systems
    presented here. 
    }
  \todo{PAVEL: include the number of$\Gamma$-surface access.} \\
\end{figure}
